Chaotic mixing of tidal debris

### 2015-06-22 ms.tex
words about new figures

We repeat the above analysis of the short-time evolution of frequencies for all orbits in the orbit grid used above (Section~\ref{sec:results1}): for each orbit, we integrate for 80 orbital periods, but compute the frequencies now in a rolling window along this integration time. We fix the window width to 40 orbital periods and shift the window by 0.5 orbital periods between each computation of the frequencies. For each orbit, we have the three frequencies (and amplitudes), $k=1,2,3$, computed at times $j$. We compute the fractional amplitude of the frequency variation for a given orbit as
\begin{equation}
	A_\Omega = \max_{a_k} \left(\frac{\max_j \Omega^{(j)}_{k} - \min_j \Omega^{(j)}_{k}}{2 \, \mean{\Omega^{(j)}_{k}}_j}\right) \label{eq:frac-freq-amp}
\end{equation}
where, as in Equation~\ref{eq:fdtime}, the outer maximum is taken with respect to the amplitude of the frequency in the power-spectrum, $a_k$, and the inner maximum and minimum are taken over time, $j$. This is a measure of the magnitude of the short-time frequency evolution for a single orbit. For tidal debris with small spreads in orbital properties, nearby orbits will have similar behavior; for example, the central marker in Figure~\ref{fig:fdiff-zooms} shows the size of a globular-cluster-like system in configuration space. When the magnitude of the short-time frequency variability is comparable to the spread in orbital frequencies within the debris, the debris effectively has a larger spread in frequencies (the effective frequency distribution is the convolution of the initial spread with a distribution that scales with the scale-length of the short-time variation). Therefore, the debris will ``fan'' or spread out over a few dynamical times and appear dynamically hotter.

\todo{apw}{new figure and paragraph repeating this for an ensemble of orbits, with frequencies for each ensemble orbit computed in the windows. show that final distribution of frequencies is spread more for weakly chaotic orbit (still waiting for queued code to finish on the cluster...)}

>>>>

We repeat the above analysis of the short-time evolution of frequencies for all orbits in the orbit grid used above (Section~\ref{sec:results1}): for each orbit, we integrate for 80 orbital periods, but compute the frequencies now in a rolling window along this integration time. We fix the window width to 40 orbital periods and shift the window by 0.5 orbital periods between each computation of the frequencies. For each orbit, we have the three frequencies (and amplitudes), $k=1,2,3$, computed at times $j$. We compute the fractional amplitude of the frequency variation for a given orbit as
\begin{equation}
	A_\Omega = \max_{a_k} \left(\frac{\max_j \Omega^{(j)}_{k} - \min_j \Omega^{(j)}_{k}}{2 \, \mean{\Omega^{(j)}_{k}}_j}\right) \label{eq:frac-freq-amp}
\end{equation}
where, as in Equation~\ref{eq:fdtime}, the outer maximum is taken with respect to the amplitude of the frequency in the power-spectrum, $a_k$, and the inner maximum and minimum are taken over time, $j$. This is a measure of the magnitude of the short-time frequency evolution for a single orbit. For tidal debris with small spreads in orbital properties, we expect nearby orbits to have similar behavior; for example, the central marker in Figure~\ref{fig:fdiff-zooms} shows the size of a globular-cluster-like system in configuration space. We therefore expect a small ensemble of orbits in frequency space to expand over short times around even weakly chaotic parent orbits and the debris will therefore appear dynamically hotter in real-space.

We illustrate this phenomenon by repeating the above experiment for small ensembles of orbits around each parent orbit. As before, we compute the frequencies of each orbit in a series of overlapping windows to resolve the short-time evolution of the frequencies. Figures~\ref{fig:regular-ensemble-freq-evolution}--\ref{fig:chaotic-ensemble-freq-evolution} show the evolution of the frequencies for all orbits in each ensemble generated around the three orbits, R, W, and S. In all panels in each of these figures, whats plotted are the per cent deviations of each frequency ratio from the parent orbit frequency ratios computed in the first time window. The left panels in each figure show these per cent deviations for all ensemble orbits around each of the three orbits. Middle panels show the full evolution of each ensemble orbit over 16 orbital periods, and final panel shows the final per cent deviations for all ensemble orbits (after 16 orbital periods). Note that the axis scales are quite different between each figure --- the strongly chaotic orbit ensemble evolves quickly due to its proximity to many overlapping resonances.
